### 2021-04-21 input/background.tex
ref fix
reworkd background

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. \TODO{Meow.}

\end{asparadesc}

>>>>

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \processes that belong to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partition would block the
propagation of other partitions.
\end{asparadesc}

Next Section details adaptive scoped broadcast in dynamic networks. It
details the properties of such protocol, and provides an
implementation along with its complexity.
